Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-08-08 main.tex
Update on Overleaf.

One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}. While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging. More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects. How to properly account for multi-phase mixing, however, is still poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018} 
% KVJ: citations to high-redshift work in this area
\textbf{and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.} Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.

@@

It is becoming increasingly valuable to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}. Stellar abundances are directly imprinted with the enrichment pattern of their star-forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM. The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM. Furthermore, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history. 
% KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
\textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Freeman2002,Ting2012, Hogg2016,Jofre2017,Price-Jones2018}. Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations. Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.}

@@

The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity. Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging. 
[list examples of modelling problems]. 
These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study. By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars. In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons. First, we would like to build our understanding of galactic chemical evolution from a fundamental level. Second, there is only a severly limited sample of gas-rich dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here. This work will be the first of several attempting to bridge this gap. With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.

@@

\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually. Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse SNe at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution. Stars above this mass are assumed to direct collapse with no mass or energy injection. For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}. We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars. Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind \citep{Goldman2017}. Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia SN progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields. Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et. al. in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.

@@

We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the metal fraction  PDFs of individual elements in galaxy models. The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM. In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions. Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$. As this is the source of star-forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.

@@

\subsection{Physical Interpretation of the PDF}
\label{sec:interpretation}
%
% KVJ wanted clarification on this argument. I believe my added text 
% does this sufficiently.
Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_{\rm o}$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$. Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas. In this case, $p(t,Z)$ initially takes the form of a double-delta function
\begin{equation}
p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
\end{equation}
%mm [edited the rest of this paragraph, and the next though I don't think there are any substantive changes unmarked.]
If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas. \textbf{At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$. Then, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas. \textbf{The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.}

\textbf{Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
%mm , or $p(Z)$, 
of these many events will be $\delta(Z_{\rm o})$ plus a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.}
% and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
The slope of the power-law, then, is determined by the rate of injection versus mixing with the ambient medium. A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium. Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than 
%mm enrichment. 
         injection.
If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.

@@

\textbf{cite sarmento and others (see BWO comments)}
Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}. Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion. This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dense gas ($\sim$ 1 km s$^{-1}$). Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy. This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas. It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing SNe. Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star-forming gas. Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy. The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.

@@

To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected by AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times. This model was run using \textsc{SYGMA} \citep{Ritter2017}. As shown, metal enrichment from AGB winds only begins to dominate for any elements after $\sim$ 100 Myr. This includes N and Ba, which we follow in our simulations, but this model predicts that Ag and Pb will show similar bahavior. It takes over a gigayear for C to be dominated by AGB wind ejecta, which is the case for many of the elements shown. F, which shows very little contribution from AGB winds at short timescales, is dominated by enrichment from them on longer timescales. These dependences on metallicity and timescales certainly add complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales. Clearly this motivates future work covering gigayear timescales to fully understand how metal mass fraction PDFs evolve with time.

@@

%KVJ suggested emphasizing that there is much more potential in this work / work like this by examining more dimensions
\textbf{We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework. However, the cross-correlation of multiple metal fractions and abundance ratios is the most useful in revealing key processes in galactic chemodynamics. A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiements. We will examine this more complicated multi-dimensional space with these numerical methods in future work.}

@@

\subsection{Do These Results Apply to More Massive Galaxies?}
\label{sec:massive galaxies}
An important caveat about our work is that these results are derived from simulations of an isolated, low mass, dwarf galaxy whose properties vary dramatically from more massive galaxies like the Milky Way. It is unclear how much these results apply to more massive galaxies with deeper potential wells and higher star formation rates. Feedback-driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas. We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy. With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate. \textbf{We anticipate three potential regimes of metal retention, depending on dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB stars and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.}. If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
% AE: rewording given Benoits suggested changes
%     If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
This difference would be greater at later times, once AGB enrichment becomes significant. 
%     Benoit suggested limiting / eliminating discussion relative to metallicity, since this is a little murky (age-metallicity varies significantly galaxy-to-galaxy). In addition, the elevated signals of Ba abundance ratios I mention have some amount of contention....
%     For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}. At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way. Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way. In addtion, recent observations find elevationd [Ba/Fe] vs. [Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS}, which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs. Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research. 
We would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.

@@

\section{Conclusions}
\label{sec:conclusions}
We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM. This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze for the first time how individual metal species couple to the ISM and galactic wind of this galaxy.

@@

\section{Density PDF}
\label{appendix:density PDF}
We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}. We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right. As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution. The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.   The volume weighted PDF is much better described as a multi-component power law. The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities. These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.

>>>>

One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}. While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging. More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects. How to properly account for multi-phase mixing, however, is still poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parametric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018} 
% KVJ: citations to high-redshift work in this area
%\textbf{
and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.
%}
Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.

@@

It is becoming increasingly valuable to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}. Stellar abundances are directly imprinted with the enrichment pattern of their star-forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM. The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM. Furthermore, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history. 
% KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
%\textbf{
One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Freeman2002,Ting2012, Hogg2016,Jofre2017,Price-Jones2018}. Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations. Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.

@@

The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity. Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging. 
%[list examples of modeling problems]. 
These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study. By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars. In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons. First, we would like to build our understanding of galactic chemical evolution from a fundamental level. Second, there is only a severly limited sample of gas-rich dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here. This work will be the first of several attempting to bridge this gap. With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.

@@

\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually. Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse SNe at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution. Stars above this mass are assumed to direct collapse with no mass or energy injection. For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}. We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars. Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind \citep{Goldman2017}. Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia SN progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields. Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, Slemer et. al. in prep for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.

@@

We argue here that the log-normal + power-law PDF can be a powerful tool for modeling the metal fraction  PDFs of individual elements in galaxy models. The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM. In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions. Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$. As this is the source of star-forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.

@@

\subsection{Physical Interpretation of the PDF}
\label{sec:interpretation}
%
% KVJ wanted clarification on this argument. I believe my added text 
% does this sufficiently.
Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_{\rm o}$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$. Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas. In this case, $p(t,Z)$ initially takes the form of a double-delta function
\begin{equation}
p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
\end{equation}
%mm [edited the rest of this paragraph, and the next though I don't think there are any substantive changes unmarked.]
If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas. At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$. Then, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$. This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas. The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.

Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
%mm , or $p(Z)$, 
of these many events will be $\delta(Z_{\rm o})$ plus a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.
% and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
The slope of the power-law, then, is determined by the rate of injection versus mixing with the ambient medium. A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium. Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than 
%mm enrichment. 
         injection.
If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.

@@

Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012,Sarmento2017,Sarmento2018}. Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion. This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dense gas ($\sim$ 1 km s$^{-1}$). Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy. This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas. It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing SNe. Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star-forming gas. Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy. The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.

@@

To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected by AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times. This model was run using \textsc{SYGMA} \citep{Ritter2017}. As shown, metal enrichment from AGB winds only begins to dominate for any elements after $\sim$ 100 Myr. This includes N and Ba, which we follow in our simulations, but this model predicts that Ag and Pb will show similar behavior. It takes over a gigayear for C to be dominated by AGB wind ejecta, which is the case for many of the elements shown. F, which shows very little contribution from AGB winds at short timescales, is dominated by enrichment from them on longer timescales. These dependences on metallicity and timescales certainly add complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales. Clearly this motivates future work covering gigayear timescales to fully understand how metal mass fraction PDFs evolve with time.

@@

%KVJ suggested emphasizing that there is much more potential in this work / work like this by examining more dimensions
We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework. However, the cross-correlation of multiple metal fractions and abundance ratios is the most useful in revealing key processes in galactic chemodynamics. A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiments. We will examine this more complicated multi-dimensional space with these numerical methods in future work.

@@

\subsection{Do These Results Apply to More Massive Galaxies?}
\label{sec:massive galaxies}
An important caveat about our work is that these results are derived from simulations of an isolated, low mass, dwarf galaxy whose properties vary dramatically from more massive galaxies like the Milky Way. It is unclear how much these results apply to more massive galaxies with deeper potential wells and higher star formation rates. Feedback-driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas. We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy. With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate. We anticipate three potential regimes of metal retention, depending on dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB stars and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM. If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
% AE: rewording given Benoits suggested changes
%     If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
This difference would be greater at later times, once AGB enrichment becomes significant. 
%     Benoit suggested limiting / eliminating discussion relative to metallicity, since this is a little murky (age-metallicity varies significantly galaxy-to-galaxy). In addition, the elevated signals of Ba abundance ratios I mention have some amount of contention....
%     For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}. At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way. Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way. In addtion, recent observations find elevationd [Ba/Fe] vs. [Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS}, which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs. Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research. 
We would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.

@@

\section{Conclusions}
\label{sec:conclusions}
We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM. This high resolution simulation, coupled with our star-by-star modeling of stellar nucleosynthetic yields, has allowed us to analyze for the first time how individual metal species couple to the ISM and galactic wind of this galaxy.

@@

\section{Density PDF}
\label{appendix:density PDF}
We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}. We show the mass-weighted PDF ($dm/Mdn$) on the left, and the volume-weighted PDF ($dv/Vdn$) on the right. As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution. The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.   The volume weighted PDF is much better described as a multi-component power law. The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities. These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
